\section{Getting back on track}
% 13 pages
Though planning can help structure the collaboration, it can also add quite a bit of overhead. One should therefore carefully select which planning methods to use and the extent of the planning. If you spend too much time on planning, you might not meet the deadline with all requirements satisfied, and if you spend too little time planning, the project might derail further.

In the following sections we will apply project management theory to re-plan the second part of the derailed project. We will discuss alternative development methodologies and pick the ones we believe suits the project the best, reflecting upon our results of doing so where possible.

We will not discuss the technical aspects of the second project part, although we shortly will mention that we have decided to use only languages and technologies well known to the group.
A significant cause of problems in the first part of the project stemmed from the many new tools we had decided to use without reserving the time for unforeseen problems.
In the second part of the project we do not have time to spare for such problems and have therefore decided to play safe by sticking to the well-known.

\input{texts/GettingBackOnTrack/PlanningSecondHalf.tex}
\input{texts/GettingBackOnTrack/MethodOfDevelopment.tex}
\input{texts/GettingBackOnTrack/EstimationMethods.tex}
\input{texts/GettingBackOnTrack/MethodsForPlanningTheTime.tex}
\input{texts/GettingBackOnTrack/QualityAssurance.tex}
%\subsection{Summary}
%First step was to plan the rest of the project. We used the SCRUM artifact Backlog to get an overview. We estimated work hours for each item on the backlog, to further enhance our overview. This gave us an estimate of the number of remaining hours. We also planned our available hours. Comparing our available working hours with the hours remaining in the project, showed us that we had just enough time, assuming our estimates rang true. ``The project is not derailed then?'' you might ask, and it was: We planned a lot more available hours in order to meet the project's remaining hours.
\newpage