\section{Introduction}
% 0.5 page
This paper is written for the course `System Development and Project Organization, BSUP' at ITU in the spring 2013.

In almost every software development project some degree of planning and application of development methods is needed - the need for those rises with the size of the project group, the project size, and critical factors. For larger projects the right choices of planning and development methods are essential for meeting the requirements and deadlines.\\
When a project goes of track it is essential to know how to get it back on track in order to complete the project with minimal costs and delays. % Obvious?

When a project has derailed, it can be difficult get it back up and running. One must review and adjust the chosen methods used for the project to avoid another derail. This involves discovering why the project derailed in the first place.
Once the work process has been adjusted, changes to the project plan are necessary in order to finish the project on time and with desirable quality. If nothing is done, the project will probably not be finished within the designated time frame.

In this paper we will consider a derailed project. We will find and apply the (hopefully) right methods to get it back on track and enable it to be delivered on time.

At first, we will analyze the derailed project, finding out what went wrong, and why it did so. Afterwards we will find relevant methods to `rescue' the project. At the end we will discuss the results and conclude upon our results.
\newpage